---
title: "Case study: Norway"
author: "Ayoub Belemlih"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using geogit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(tidyverse)
library(magrittr)
library(ggplot2)
library(geogit)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this example, I will retrieve data about the 300 most followed users in Norway and visualize some characteristics of their repositories.

Note: `eval` will be set to FALSE for the code chunks below. I suggest adding a GitHub personal access token to increase the API rate limit before running these chunks.

### Import Data

Import the usernames of the 300 most followed users in Norway:

```{r, eval = FALSE}
tk <- geogit_token(Sys.getenv("GITHUB_TK"))

norway_usernames <-
  geogit_location("Norway", tk, page = 1) %>%
  rbind(geogit_location("Norway", tk, page = 2)) %>%
  rbind(geogit_location("Norway", tk, page = 3))

norway_usernames <- norway_usernames$login
```

Add details to each user from `norway_users`

```{r, eval=FALSE}
norway_users <- tibble()
for (usr in norway_usernames) {
  usr_info <- 
    geogit_user(usr, tk) %>% 
    select(login, created_at, public_repos, followers, following)
  norway_users <- 
    norway_users %>% 
    rbind(usr_info)
}
norway_users %>% head(10)
```

Import the repositories tied to the users in `norway_users` (A maximum of 100 repositories per user):

```{r, eval=FALSE}
norway_users_repos <- tibble()
for (usr in norway_users$login) {
  norway_users_repos <- 
    norway_users_repos %>%
    rbind(geogit_repos(usr, tk))
}
```

Add the top language of each user, defining top language as the programming language a user used the most in the last 100 repositories they created:

```{r, eval=FALSE}
get_top_lang <- function(usr_login) {
  norway_users_repos %>%
    filter(owner == usr_login) %>%
    group_by(language) %>%
    summarise(total = n()) %>%
    arrange(desc(total)) %>%
    pull("language") %>%
    extract(1)
}

norway_users$top_lang <- 
  norway_users$login %>% 
  map(get_top_lang) %>%
  flatten_chr()
```

Add the total number of stars a user received across all the repositories they created:

```{r, eval=FALSE}
get_stars <- function(usr_login) {
  norway_users_repos %>%
    filter(owner == usr_login & fork == FALSE) %>%
    pull("stargazers_count") %>%
    sum()
}

norway_users$total_stars <- 
  norway_users$login %>% 
  map(get_stars) %>%
  flatten_int()
```

### Visualizations

30 most "starred" users in Norway (sorting by total number of stars across all repositories):

```{r, eval=FALSE}
norway_users %>%
  arrange(desc(total_stars)) %>%
  head(30) %>%
  ggplot(aes(x = reorder(login, total_stars), y = total_stars)) + 
    geom_bar(fill = "#228B22", stat = "identity") +
    labs(title = "Most Starred Users in Norway", x = "Usernames", y = "Number of Stars") +
    coord_flip()
```

30 most followed GitHub users in Norway:

```{r, eval=FALSE}
norway_users %>%
  arrange(desc(followers)) %>%
  head(30) %>%
  ggplot(aes(x = reorder(login, followers), y = followers)) + 
    geom_bar(fill = "#228B22", stat = "identity") +
    labs(title = "Most Followed Users in Norway", x = "Usernames", y = "Number of Followers") +
    coord_flip()
```

30 most popular languages in open source development in Norway, as measured by the most used language `top_lang` for each user:

```{r, eval=FALSE}
norway_users %>%
  filter(!is.na(top_lang)) %>%
  group_by(top_lang) %>%
  summarise(total = n()) %>%
  arrange(desc(total)) %>%
  head(30) %>%
  ggplot(aes(x = reorder(top_lang, total), y = total)) + 
    geom_bar(fill = "#228B22", stat = "identity") +
    labs(title = "Most Popular Programming Languages in Norway", x = "Programming Languages", y = "Number of Users") +
    coord_flip()
```


